% Hands on Systems Programming C++
\newglossaryentry{api}
{
   name={API},
   description={An Application Programming Interface (API) is a particular set
           of rules and specifications that a software program can follow to access and make use of the services and resources provided by another particular software program that implements that API},
   first={Application Programming Interface (API)},
   long={Application Programming Interface}
}

\newglossaryentry{staticlib}
{
	name={Static libraries},
	description ={
			libraries that are linked at compile time
	}
}

\newglossaryentry{dynamiclib}
{
	name={Dynamic libraries},
	description ={
			libraries that are linked at run time
	}
}

%%% Laravel Notes

\newglossaryentry{depInj}
{
	name={Dependency Injection},
	description={
		Dependency injection means that, rather than being instantiated ("newed up") within a class, each class's dependencies will be injected in from the outside.
	}
}

\newglossaryentry{IoC}
{
	name={IoC},
	description={
		In software engineering, inversion of control (IoC) is a programming principle. IoC inverts the flow control as compared to traditional control flow. In IoC, custom-written portions of a computer program receive the flow of control from a generic framework. A software architecture with this design inverts control as compared to traditional procedural programming: in traditional programming, the custom code that expresses the purpose of the program calls into reusable libraries to take care of generic tasks, but with inversion of control, it is the framework that calls into the custom, or task-specific, code.
	},
	first={Inversion of Control},
	long={Inversion of Control}
}

%% --- GAN Notes ---
\newglossaryentry{GAN}
{
	name={GAN},
	description={
		A GAN is a deep neural network architecture made up of two networks, a generator network and a discriminator network. Through multiple cycles of generation and discrimination, both networks train each other, while simultaneously trying to outwit each other.
	},
	first={Generative Adversarial Networks},
	long={Generative Adversarial Networks}
}
% --- Software Tools ---
\newglossaryentry{git}
{
	name={git},
	description ={
			the most popular version control system used for tracking changes in source code and coordinating work on those files among multiple people
	}
}

% --- Quantum Computing ---


% --- Algorithms ---
\newglossaryentry{Adapter}
{
	name = {Adapter},
	description = {
		The adapter pattern provides a wrapper with an interface
		required by the \gls{api} client to link incompatible types and act as a
		translator between the two types. The adapter uses the interface
		of a class to be a class with another compatible interface. When
		requirements change, there are scenarios where class
		functionality needs to be changed because of incompatible
		interfaces.
	}
}

\newglossaryentry{Bridge}
{
	name={Bridge},
	description={
			Bridge decouples the implementation from the abstraction. The
		abstract base class can be subclassed to provide different
		implementations and allow implementation details to be
		modified easily. 
	}
}

%%%%%%%%%%%%%%%%% BRIDGE GAME %%%%%%%%%%%%%%%%%%%%


% Finance Terms
\newglossaryentry{DebtToEquity}
{
	name={Debt To Equity},
	description={
		The debt-to-equity (D/E) ratio indicates how much debt a company is using to finance its assets relative to the value of shareholders' equity.
	}
}

\newglossaryentry{DeadCatBounce}
{
	name={Dead Cat Bounce},
	description={
		Dead cat bounce is a small, brief recovery in the price of a declining stock.
	}
}